Model-based variable selection for regression with highly correlated variables.

### 2014-04-17 www/article13.tex
up title
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@544 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
new title
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@545 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[table]{xcolor}
 \graphicspath{{figures/}}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
%\author{Clément THERY, Christophe BIERNACKI, Gaétan LORIDANT}
\title{Model-based pretreatment for regression with correlated variables.}

@@

\begin{document}
\begin{center}
{\Large
	{\sc Model-based pretreatment for regression \\ with correlated variables.}
}
\bigskip

@@

	With the rise of informatics, datasets contain more and more covariates,% and thus dimension reduction becomes a necessity. Moreover, 
	increasing the chance to have correlated ones.  It will be illustrated with examples from steel industry in the last section of this paper (many parameters of the whole process without any a priori) highly correlated (physical laws, process rules, etc). 
	 In such a context, variance of the estimators can lead to arbitrary results whereas interpretation and prediction are both strongly needed, depending on the context. For instance, in an industrial context interpretation could be favoured to improve the process instead of only predict defects, so robust estimation is needed.
		~\\	~\\

%bibliographie	
	Because \textsc{OLS} is the minimum-variance linear unbiased estimator, other methods can be seen as a pretreatment on the dataset to improve $\boldsymbol{X}'\boldsymbol{X}$ conditioning (by introducing some bias, selecting only some covariates, grouping some covariates, {\it etc.}).

@@

	 Penalized methods try to reduce the variance introducing some bias to improve the bias-variance trade-off and get better prediction.
	Ridge regression \cite{marquardt1975ridge} proposes a biased estimator that can be written in terms of a parametric $L_2$ penalty:
	\begin{equation}
		 \boldsymbol{\hat{\beta}}=\operatorname{argmin} \left\lbrace \parallel \boldsymbol{Y}-\boldsymbol{X\beta}\parallel_2^2 \right\rbrace \textrm{ subject to } \parallel \boldsymbol{\beta} \parallel_2^2\leq \lambda \textrm{ with } \lambda>0
	\end{equation}
	But this penalty is not guided by the correlations. It is the same for each covariates and will be too large for independent covariates and/or too small for correlated ones. So the efficiency of such a method is limited. 
	Moreover, coefficients tend to 0 but don't reach 0 so it gives difficult interpretations for large values of $p$.

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[table]{xcolor}
 \graphicspath{{figures/}}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
%\author{Clément THERY, Christophe BIERNACKI, Gaétan LORIDANT}
\title{Model-based variable selection for regression with highly correlated variables.}

@@

\begin{document}
\begin{center}
{\Large
	{\sc Model-based pretreatment for regression \\ with highly correlated variables.}
}
\bigskip

@@

	With the rise of informatics, datasets contain more and more covariates, % and thus dimension reduction becomes a necessity. Moreover, 
	increasing the chance to have correlated ones.  It will be illustrated with examples from steel industry in the last section of this paper (many parameters of the whole process without any a priori and highly correlated: physical laws, process rules, etc). 
	 In such a context, variance of the estimators can lead to arbitrary results whereas interpretation and prediction are both strongly needed, depending on the context. For instance, in an industrial context interpretation could be favoured to improve the process instead of only predict defects, so robust estimation is needed.
		~\\	~\\

%bibliographie	
	Because \textsc{OLS} is the minimum-variance linear unbiased estimator, some other methods can be seen as a modification of the dataset to improve the robustess of the estimator (by introducing some bias, selecting only some covariates, grouping some covariates, {\it etc.}).

@@

	 Penalized methods try to reduce the variance introducing some bias to improve the bias-variance tradeoff and get better prediction.
	Ridge regression \cite{marquardt1975ridge} proposes a biased estimator that can be written in terms of a parametric $L_2$ penalty:
	\begin{equation}
		 \boldsymbol{\hat{\beta}}=\operatorname{argmin} \left\lbrace \parallel \boldsymbol{Y}-\boldsymbol{X\beta}\parallel_2^2 \right\rbrace \textrm{ subject to } \parallel \boldsymbol{\beta} \parallel_2^2\leq \lambda \textrm{ with } \lambda>0
	\end{equation}
	But this penalty is not guided by the correlations. It is the same for each covariates and will be too large for independent covariates and/or too small for correlated ones. So the efficiency of such a method is limited. 
	Moreover, coefficients tend to 0 but don't reach 0 so it gives difficult interpretations for large values of $p$.
